\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-08-15 onebit_full.tex
small changes

\subsubsection*{Sketch of Proof}
The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$. Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are in Appendix~\ref{proof:thm:adpative_lower_bound}.\par

@@

Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}. %Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$. 
%
The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$. Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$. The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum. In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}. Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment. 
 \par
%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}. A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization. Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.  \\
In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$. In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
%
As we explain next, 
it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.

@@

\subsection{Optimality using One Round of Threshold Adaptation}
In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
\[
B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
\]
and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
%
We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ at least once. 
%
In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$. Figure~\ref{fig:one_round} illustrates a diagram of this procedure. 
%
The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
\begin{thm}
For $i=1,\ldots,n$ set
\[
B_i = \begin{cases}
 \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
 \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
\end{cases}
\]
where $n = n_1+ n_2$ and 
\[
{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
 \right).
\] 
Let 
\[
{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
\]
and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
\begin{align*}
 \sqrt{n} \left( {\theta}_{n_2} - \theta  \right)^2  \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
\end{align*}
\end{thm}
%
%
\begin{proof}
For $t\in \mathbb R$, set
\[
p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
\]
From the central limit theorem
\begin{align*}
& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
\end{align*}
where
\[
V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
\]
Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ we obtain
\begin{align*}
& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
& \overset{d}{\to} \Ncal\left(0, 
1/\eta(\theta-t) \right).
\end{align*}
%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
By the law of large numbers we also have
\[
p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
\]
so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
\[
\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
\]
By Slutsky's theorem we get
\begin{align*}
& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
& \overset{d}{\to} \Ncal\left( 0, 
1/\eta(0) \right). 
\end{align*}
\end{proof}
%

@@

\section{Distributed Estimation \label{sec:distributed}}
We now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii). In this setting each one-bit message $B_i$ is only a function of its private sample $X_i$, and hence $B_i$ characterized by its \emph{detection region}, defined as 
\[
A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
\]
Consequently, $B_i$ is of the form
\[
B_i = \begin{cases} 1 & X_i \in A_i, \\
-1 & X_i \notin A_i,
\end{cases} \quad i\in \mathbb N,
\]
where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par

@@

\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin = 0, xmax=2, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 10,
samples=1, 
xlabel= {$\sigma/\sigma_\theta$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,1.5708,5},
yticklabels={0,$\pi/2$,5},
ylabel = {$R_{\pi}^\star/\sigma^2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
\addplot[color = black, dashed] {3.14159 / 2};
\end{axis}
\end{tikzpicture}
\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$. 
%
%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}. It is illustrated for various cases in Fig.~\ref{fig:opt_density}. The dashed curve represents the upper bound \eqref{eq:upper_bound}. 
\label{fig:dist_bound_uniform}  }
\end{center}
\end{figure}

As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution. In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}. As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$. 
 \eqref{eq:cvx_average}. 
\begin{prop}\label{prop:upper_bound}
For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
\begin{equation} 
\label{eq:upper_bound}
R_\pi^\star  \leq 
 \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
\end{equation}
Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
\begin{equation}
\label{eq:bound_Taylor}
R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
\end{equation}
\end{prop}
\begin{proof}
The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
\[
\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
\]
Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
\begin{align}
\mathbb E  \frac{1}{\kappa(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
\end{align}
The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$. Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
%\[
%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
%\]
and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
\end{proof}
We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so taking $\theta_0 = \mathbb E \theta$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$. The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.

>>>>

\subsubsection*{Proof}
%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$. The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are in
See Appendix~\ref{proof:thm:adpative_lower_bound}.\par

@@

Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}. %Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$. 
%
The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$. Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$. The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum. In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}. Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment. 
 \par
%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}. A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization. Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.  \\
In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$. In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
%
As we explain next, 
it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.

@@

\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
\[
B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
\]
and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
%
We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once. 
%
In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$. Figure~\ref{fig:one_round} illustrates a diagram of this procedure. 
%
The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
\begin{thm}
For $i=1,\ldots,n$ set
\[
B_i = \begin{cases}
 \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
 \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
\end{cases}
\]
where $n = n_1+ n_2$ and 
\[
{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
 \right).
\] 
Let 
\[
{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
\]
and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
\begin{align*}
 \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
\end{align*}
\end{thm}
%
%
\begin{proof}
For $t\in \mathbb R$, set
\[
p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
\]
From the central limit theorem
\begin{align*}
& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
\end{align*}
where
\[
V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
\]
Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
\begin{align*}
& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
& \overset{d}{\to} \Ncal\left(0, 
1/\eta(\theta-t) \right).
\end{align*}
%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
On the other hand, by the law of large numbers,
\[
p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
\]
so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
\[
\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
\]
Finally,
\begin{align*}
& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
& \overset{d}{\to} \Ncal\left( 0, 
1/\eta(0) \right) 
\end{align*}
by Slutsky's theorem.
\end{proof}
%

@@

\section{Distributed Estimation \label{sec:distributed}}
In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$. In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as 
\[
A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
\]
Consequently, $B_i$ is of the form
\[
B_i = \begin{cases} 1 & X_i \in A_i, \\
-1 & X_i \notin A_i,
\end{cases} \quad i\in \mathbb N,
\]
where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par

@@

\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin = 0, xmax=2, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 10,
samples=1, 
xlabel= {$\sigma/\sigma_\theta$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,1.5708,5},
yticklabels={0,$\pi/2$,5},
ylabel = {$R_{\pi}^\star/\sigma^2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
\addplot[color = black, dashed] {3.14159 / 2};
\end{axis}
\end{tikzpicture}
\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$. 
%
%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}. It is illustrated for various cases in Fig.~\ref{fig:opt_density}. The dashed curve represents the upper bound \eqref{eq:upper_bound}. 
\label{fig:dist_bound_uniform}  }
\end{center}
\end{figure}

As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution. In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}. As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$. 
 \eqref{eq:cvx_average}. 
\begin{prop}\label{prop:upper_bound}
For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
\begin{equation} 
\label{eq:upper_bound}
R_\pi^\star  \leq 
 \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
\end{equation}
Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
\begin{equation}
\label{eq:bound_Taylor}
R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
\end{equation}
\end{prop}
\begin{proof}
The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
\[
\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
\]
Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
\begin{align}
\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
\end{align}
The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$. Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
%\[
%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
%\]
and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
\end{proof}
We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$. The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
